---
title: "exercise_02"
author: "Magdalena Wagner"
format: pdf
editor: visual
---

# Problem 1

# weight data from participants in kg

```{r}
weight <- c(
61, 60, 73, 69, 82, 85, 52, 91, 68, 50, 108, 81, 52, 57, 85, 74,
65, 56, 69, 58, 94, 64, 62, 58, 50, 50, 83, 62, 53, 81, 82, 84,
60, 72, 95, 89, 75, 61, 53, 82, 74, 67, 60, 80, 64, 60, 71, 78,
90, 74, 59, 85, 87, 75, 100, 85, 71, 60, 72, 62, 65, 95 , 83, 62
) 
```

## 1.1 What is the mean, maximum, and minimum weight of the weight data?

```{r}
mean(weight) 
range(weight)
```

## 1.2 Calculate the mean of the weight data “by hand”.

```{r}
mean(c, na.rm = TRUE)
```

##1.3 Create a new vector that contains the minimum and the maximum of the weight data.

```{r}
mean(c, na.rm = TRUE)
```

## 1.4 What is the standard deviation and variance of the weight data?

```{r}
sd(weight)
var(weight)
```

## 1.5 What is the height that 50% of the participants surpass and 50% fall below?

```{r}
mean(c, na.rm = TRUE)
```

## 1.6 What is the weight that only 25% of the participants surpass?

```{r}
mean(c, na.rm = TRUE)
```

## 1.7 Increase the weight of every participant by 20% and assign the result to a new object.

```{r}
mean(c, na.rm = TRUE)
```

# Problem 2

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 2.1 Convert names to uppercase.

```{r}
toupper("names")
```

## 2.2 Create participant IDs (P_1, P_2, P_3, …) in a way that it could be applied to any number of names. hint: use paste() and rep().

```{r}
names <- c("anna", "ben", "chris", "diana")
```

# Problem 3

## 3.1 Create a list named participant_info that contains the following:
• ID: 101
• Name: Alex
• Age: 25
• Scores: A vector of test scores: 85, 90, 78, 92
• Diagnosis: A list with:
– Has_Anxiety: TRUE (logical value indicating anxiety presence)
– Severity: “Moderate Anxiety”

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 3.2 Access and print the second test score and the Diagnosis list with the Severity element.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 3.3 Change Has_Anxiety to FALSE and remove the Severity element.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 3.4 Append a new score 88 to the Scores vector.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 3.5 Calculate the sum of the Scores.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

# Problem 4

## 4.1 Create a 3D array called psych_array with 2 rows, 3 columns, and 3 layers. The array should contain random numbers between 1 and 100.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 4.2 Label the rows, columns, and layers:
• Rows: Participant_1, Participant_2
• Columns: Stress, Anxiety, Depression
• Layers: Time_1, Time_2, Time_3 (simulating repeated measures over time)
Hint: Pass a list to dimnames.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 4.3 Access and print the stress level of Participant_1 at Time_2 and the entire Anxiety column for all time points.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 4.4 Sum the Depression levels at Time_2 and Time_3 for both participants and subtract the result from Time_1.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

# Problem 5

## 5.1 Create a data frame called psych_study with 100 participants, containing the following columns:
• Participant_ID: A sequence of numbers from 1 to 100.
• Age: Random ages between 18 and 60.
• Gender: Randomly assign “Male”, “Female”, or “Non-binary” with probabilities 0.45, 0.45, 0.1.
• Stress_Level: Random values from a normal distribution with a mean of 5 and standard deviation of 2.
• Anxiety_Score: A score from 0 to 10, generated using rbinom(). Assume 10 trials with a probability of 0.4
• Therapy_Attendance: A binary variable (0 = No, 1 = Yes) indicating whether the participant has attended therapy (hint: use rbinom()).

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 5.2 Calculate:
• The mean and standard deviation of Stress_Level.
• The proportion of participants who have attended therapy.
• The average Anxiety Score for those who have attended therapy

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 5.3 Convert the Therapy_Attendance variable to a factor with labels “No” and “Yes”.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 5.4 Round the Stress_level to an integer (no decimals) and get the number of unique values.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 5.5 Create a new subset of the data where:
• Stress_Level is greater than 5
• Anxiety_Score is greater than or equal to 5
• and the person has not attended therapy
Store this in high_risk_group.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 5.6 Mean-center the Stress_Level variable.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 5.7 Compute the average Stress_Level and Anxiety_Score for each gender.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

## 5.8 Compute the percentage of therapy attendees per gender.

```{r}
names <- c("anna", "ben", "chris", "diana")
```

